Data-driven approaches to identifying knowledge gaps in marine invertebrate biodiversity

### 2017-05-30 manuscript.Rmd
use cowplot to combine richness per database plots + include in ms

@@

To assess whether species included in regional lists but absent from the same geographic area nevertheless occur elsewhere, we queried the iDigBio and OBIS database for all the marine invertebrate species included in these lists.

@@

@@

![Level of digitization for the Salish Sea](figures/plot_richness_per_db_koz.pdf)

![Level of digitization for the Gulf of Mexico](figures/plot_richness_per_db_gom.pdf)

>>>>

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

To assess whether species included in regional lists but absent from the same geographic area nevertheless occur elsewhere, we queried the iDigBio and OBIS databases for all the marine invertebrate species included in these lists.

@@

```{r database_richness, fig.cap='Comparison of the fraction of species listed in regional lists that are present in biodiversity databases for the Gulf of Mexico (A) and the Pacific Northwest (B).'}
knitr::include_graphics("figures/richness_per_db.pdf")
```

@@
